A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-20 archive/v3/docs/results_photometry_v3.01.tex
Started editing the results section.

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image, ignoring diffraction spikes. The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

@@

%============================================================================
\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}
%============================================================================

\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}. Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

%============================================================================
\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}). This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g. spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions. \Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
\label{fig:MGEouterRegions}
\end{figure}
%============================================================================

%============================================================================
\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}. The fit is best inside an radius of $5''$. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.  The first column gives the total F814W luminosity of the Gaussian in Equation \ref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \ref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \ref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}
%============================================================================

The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. \Wilma{[TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???]}

>>>>

%============================================================================
\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}
%============================================================================

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image, ignoring diffraction spikes. The one-dimensional MGE fit of Equation \eqref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}. Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

@@

The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. \Wilma{[TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g., with or without subscripts of 0, is fine???]}

%============================================================================
\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}). This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions. \Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
\label{fig:MGEouterRegions}
\end{figure}
%============================================================================

%============================================================================
\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}. The fit is best inside an radius of $5''$. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.  The first column gives the total F814W luminosity of the Gaussian in Equation \eqref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}
%============================================================================

### 2015-11-20 docs/data_v3.02.tex
Started editing the results section.

For our lensing and dynamics analysis of J1331 we use both Hubble Space Telescope (HST) imaging by \cite{SWELLSI} in two filters (F450W and F814W), as well as line-of-sight stellar kinematics along J1331's major axis by \citet{SWELLSV}.

\paragraph{Redshift.} \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}. According to its redshift and the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.

\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.  The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W to create a surface brightness MGE model of the reddish bulge (I-band), used in the JAM dynamical modelling.

\paragraph{Stellar kinematics.} For the dynamical modelling we also use the stellar kinematics for J1331 measured by \citet{SWELLSV}. They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope. The width of the slot was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$. Spectra for spatial bins of different widths along the major axis were extracted. They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission \Wilma{[TO DO: Check if really emission lines or, more likely, absorption lines]} lines in these spectra \Wilma{[TO DO: Find out which lines]}. Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for ionized gas.
\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}. The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc. Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is expected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}. However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim5''$. 
\\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data. We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.

 \Wilma{[TO DO: Maybe mention the following details better in the data section.... "SWELLS picked galaxies in SDSS whose spectra had two different redshifts within $3''$, which makes it likely to capture strong lenses with typical Einstein radii of $1''$. Sufficiently inclined galaxies were picked by eye. Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}

 \Wilma{[TO DO: Include better in data section. "of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000)"]}

>>>>

\paragraph{Redshift and position.} J1331 is located at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.

\paragraph{HST imaging.} We use HST imaging of J1331 by \citet{SWELLSI}. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness MGE model of the reddish bulge.

\paragraph{Stellar kinematics.} For the dynamical modelling we use the stellar kinematics for J1331 measured by \citet{SWELLSV}. They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope. The width of the slot was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$. Spectra for spatial bins of different widths along the major axis were extracted. They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission \Wilma{[TO DO: Check if really emission lines or, more likely, absorption lines]} lines in these spectra \Wilma{[TO DO: Find out which lines]}. Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for ionized gas.
\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}. The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc. Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is expected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}. However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim5''$. 
\\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data. We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.

 \Wilma{[TO DO: Maybe mention the following details better in the data section.... "Sufficiently inclined galaxies were picked by eye. Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}

### 2015-11-20 docs/introduction_v3.02.tex
Started editing the results section.

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000). Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e., assumes an angular diameter distance of 414 Mpc). The color scaling of these two images is the same. The black solid line in panel (b) shows the orientation of the major-axis. The line has a length of $10''$ and indicates the region within which we carry out the Jeans modelling. \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted. An IRAF \emph{ellipse} fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G). \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc. The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$. \Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Mention, that the configuration of the additional two bright blobs do not suggest that they form a lensing doublet. They are probably background star formation regions as well. The blob above A could be stretched due to lensing and have a faint counter image between B and G. Maybe indicate in plot?]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
\label{fig:specialJ1331}
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The black solid line in panel (b) shows the orientation of the major-axis. Its length is $10''$ and it indicates approximately where we carry out the dynamical modelling. \emph{Panel (c):} Lensing images in the central region of J1331.  An IRAF \emph{ellipse} fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). (The four bright blobs (A,B,C and D), that become visible, are arranged in a typical strong lensing configuration around the center of the galaxy (G). The configuration of the two additional blobs, that lie approximately on a line with A, B and G, does not suggest that they form a lensing doublet. They might be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2~\text{kpc}$. The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
\label{fig:specialJ1331}
\end{figure*}
